Probabilities of polar alignment in circumbinary disks

### 2024-12-29 src/tex/ms.tex
j_cr instead of j_crit

Figure \ref{fig:fpol_j} shows $f_\text{polar}$ as a function of $j$ for various choices of $p_{e_\text{b}}(e_\text{b})$. As expected, the curves all converge in the Kozai-Lidov regime. The uniform and thermal distributions both produce polar fractions $>0.5$ for small $j$, with the thermal distribution slightly higher. Except for when $j$ is nearly 0, the circularized $e_\text{b} < 0.1$ curve follows the $e_\text{b} = 0.01$ curve very closely, including a maximum at $j=0.5$. This feature is present to some degree in all the low-$j$ curves, and is the result of the fact that, for $e_\text{b}=0$, the critical value for $j$ is 0.5 \citet{abod2022}. The size and shape of the prograde, retrograde, and libration regions change very quickly at this value, with no retrograde orbits allowed when $j>j_\text{crit}$, except for the trivial case of $i=\pi$.

>>>>

Figure \ref{fig:fpol_j} shows $f_\text{polar}$ as a function of $j$ for various choices of $p_{e_\text{b}}(e_\text{b})$. As expected, the curves all converge in the Kozai-Lidov regime. The uniform and thermal distributions both produce polar fractions $>0.5$ for small $j$, with the thermal distribution slightly higher. Except for when $j$ is nearly 0, the circularized $e_\text{b} < 0.1$ curve follows the $e_\text{b} = 0.01$ curve very closely, including a maximum at $j=0.5$. This feature is present to some degree in all the low-$j$ curves, and is the result of the fact that, for $e_\text{b}=0$, the critical value for $j$ is 0.5 \citet{abod2022}. The size and shape of the prograde, retrograde, and libration regions change very quickly at this value, with no retrograde orbits allowed when $j>j_\text{cr}$, except for the trivial case of $i=\pi$.
